# Data transformation
## Import Data
The Department of Finance’s Rolling Sales files lists properties that sold in the last twelve-month period in New York City. We display the variables names of the datasets:
```{r}
library(tidyverse)
library(dplyr)
library(readxl)
RS_Ma <- read_excel("rollingsales_manhattan.xlsx")
RS_Bron <- read_excel("rollingsales_bronx.xlsx")
RS_Brook <- read_excel("rollingsales_brooklyn.xlsx")
RS_Que <- read_excel("rollingsales_queens.xlsx")
RS_SI <- read_excel("rollingsales_statenisland.xlsx")
names(RS_Ma)
```
Pick a dataset to take a brief look at:
```{r}
RS_Bron
```

## Data Transformation
### Combine the five tables into one
Before combine:
```{r}
summary(RS_Ma$BOROUGH)
```
After combine:
```{r}
library(hrbrthemes)
library(dplyr)
data<-rbind(RS_Ma,RS_Bron,RS_Brook,RS_Que,RS_SI)
summary(data$BOROUGH)
```




### Add one new column to the dataset and Rearrange the order of the columns

```{r}
#Describe the classification of BOROUGH in words
description <- data.frame(BOROUGH = c("1","2","3","4","5"), Name = c(
  "Manhattan",
  "Bronx",
  "Brooklyn",
  "Queens",
  "StatesIsland")
  )
#Add the new column to the dataset
new_data <- data %>%
  filter(data$BOROUGH %in% c("1","2","3","4","5")) %>%
  inner_join(., description)
#Rearrange the order of the columns
new_data<-new_data[c(1,22,2:21)]
head(new_data)
```
### Rename and display all variables name of new dataset
```{r}
new_data$BUILDING_CLASS_CATEGORY<-new_data$`BUILDING CLASS CATEGORY`
new_data$`BUILDING CLASS CATEGORY` <- NULL
new_data$RESIDENTIAL_UNITS<-new_data$`RESIDENTIAL UNITS`
new_data$`RESIDENTIAL UNITS` <- NULL
new_data$COMMERCIAL_UNITS<-new_data$`COMMERCIAL UNITS`
new_data$`COMMERCIAL UNITS` <- NULL
new_data$TOTAL_UNITS<-new_data$`TOTAL UNITS`
new_data$`TOTAL UNITS` <- NULL
new_data$LAND_SQUARE_FEET<-new_data$`LAND SQUARE FEET`
new_data$`LAND SQUARE FEET` <- NULL
new_data$GROSS_SQUARE_FEET<-new_data$`GROSS SQUARE FEET`
new_data$`GROSS SQUARE FEET` <- NULL
new_data$YEAR_BUILT<-new_data$`YEAR BUILT`
new_data$`YEAR BUILT` <- NULL
new_data$TAX_CLASS_AT_TIME_OF_SALE<-new_data$`TAX CLASS AT TIME OF SALE`
new_data$`TAX CLASS AT TIME OF SALE` <- NULL
new_data$BUILDING_CLASS_AT_TIME_OF_SALE<-new_data$`BUILDING CLASS AT TIME OF SALE`
new_data$`BUILDING CLASS AT TIME OF SALE` <- NULL
new_data$SALE_PRICE<-new_data$`SALE PRICE`
new_data$`SALE PRICE` <- NULL
new_data$SALE_DATE<-new_data$`SALE DATE`
new_data$`SALE DATE` <- NULL
#Display all variables name of new_data
names(new_data)
```

### Remove the columns and rows we don't need
Before remove:
```{r}
head(new_data)
```
Because there are some variables that are not useful for our study of house price changes in New York, and in addition to that, we do not need houses with transactions below $1,000, so we remove them.
```{r}
#Remove the columns we don't need 
new_data<-new_data[,-(4:11)]
#Remove the rows with house price less than 1000
new_data1 <- new_data[!(new_data$SALE_PRICE<1000),]
new_data1
```


